What is the Impact of Transit Developments and Shutdowns on Urban Mobility?

### 2019-10-20 proposal.Rmd
markdown fix

---
title: "What is the Impact of Transit Developments and Shutdowns on Urban Mobility?"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(sf)

travel_times <- read_csv(file = "data/boston-censustracts-2019-3-All-HourlyAggregate.csv")
shapes <- st_read(dsn = "data/boston_censustracts.json")
```

@@

Some possible events to look at:
* https://www.mass.gov/news/governor-baker-mbta-launch-ride-pilot-program-with-uber-lyft
* https://www.wbur.org/news/2015/10/07/mbta-announces-nonstop-commuter-rail-trips-between-worcester-and-boston
* https://www.wbur.org/news/2016/03/21/mbta-government-center-reopens
* https://boston.cbslocal.com/2018/04/02/mbta-early-morning-bus-service-routes/
* https://boston.cbslocal.com/2018/04/21/mbta-silver-line-chelsea-boston/
* http://www.wbur.org/news/2018/05/22/mbta-summer-weekend-commuter-rail-ten-bucks / https://www.telegram.com/news/20180906/commuter-rail-extends-10-weekend-fare-until-dec-9 / https://commonwealthmagazine.org/transportation/t-to-relaunch-10-weekend-commuter-rail-fare/

>>>>

---
title: "What is the Impact of Transit Developments and Shutdowns on Urban Mobility?"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
# library(tidyverse)
# library(sf)
# 
# travel_times <- read_csv(file = "data/boston-censustracts-2019-3-All-HourlyAggregate.csv")
# shapes <- st_read(dsn = "data/boston_censustracts.json")
```

@@

Some possible events to look at:

* https://www.mass.gov/news/governor-baker-mbta-launch-ride-pilot-program-with-uber-lyft
* https://www.wbur.org/news/2015/10/07/mbta-announces-nonstop-commuter-rail-trips-between-worcester-and-boston
* https://www.wbur.org/news/2016/03/21/mbta-government-center-reopens
* https://boston.cbslocal.com/2018/04/02/mbta-early-morning-bus-service-routes/
* https://boston.cbslocal.com/2018/04/21/mbta-silver-line-chelsea-boston/
* http://www.wbur.org/news/2018/05/22/mbta-summer-weekend-commuter-rail-ten-bucks / https://www.telegram.com/news/20180906/commuter-rail-extends-10-weekend-fare-until-dec-9 / https://commonwealthmagazine.org/transportation/t-to-relaunch-10-weekend-commuter-rail-fare/
